Fluoroproj: Title to be decided later

### 2023-07-07 manuscript/manuscript.qmd
working on grouped bar plot
making progress!

---
title: "Fluoroproj: Title to be decided later"
author: "Stephen D. Shivers, Sophie Fournier, Jakob Stankoski, Jeffrey W. Hollister, Betty J. Kreakie"
abstract: "This is our abstract.  Just seeing how it looks."
format: docx
bibliography: manuscript.bib
---

@@

Add in stuff about sampling and Phycotech.

@@

Fig 2. Chlorophyll Scatterplot

@@

Fig 3. Phyco Scatterplot

### Phycocyanin to Chlorophyll Ratio

Fig 4. Ratio Scatterplot

@@

-   Add in Phycotech data (all from 10-6)

-   When did turnover happen? Might argue against using phycotech data for 10-21 and 11-09

-   Maybe drop melville cuz to late/mismatch with phycotech.

@@

>>>>

---
title: "Fluoroproj: Title to be decided later"
author: "Stephen D. Shivers, Jeffrey W. Hollister, Sophie Fournier, Jakob Stankoski, Betty J. Kreakie"
abstract: "This is our abstract.  Just seeing how it looks."
format: docx
bibliography: manuscript.bib
---

@@

Add in stuff about sampling and Phycotech. Sampling dates of phytoplankton vs fluoro

@@

![Figure 2. Comparison of fluorometers by waterbody](images/fig2_chla_scatter.jpg)

@@

![Figure 3. Comparison of phycocyanin measurements by waterbody](images/fig3_phyco_scatter.jpg)

@@

![Figure 4. Compare Relative Biovolume of divisions by waterbody](images/fig4_rel_bio_bar.jpg)

![Figure 5. Compare Total Biovlume of divisions by waterbody](images/fig5_total_bio_bar.jpg)

Table 1. Waterbody, Cyano Genus, Relative Biovolume Total Biovolume

```{r read_tabl1, echo=FALSE, message=FALSE}
table1 <- read_csv(here::here("data/cleaned_phycotech_cyano_data.csv")) 
```

```{r show_table1, results='asis'}
knitr::kable(table1)
```

@@

## Acknowledgements

And special thanks to Gracie, Anastasia, and Lilac for emotional support during challenging analysis times.
